Untitled

### 2017-08-24 PaperCode.Rmd
Extra plots
Added in some plots which get printed to the Latex file. for weasy updating. also for tables

#number of LUPS and Total Homes
ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  filter(!is.na(LAD11NM)) %>%
  summarise(
           TotalLads = length(ls(pattern = "DATA", envir = globalenv())), #bits of other LADS cause the number to be higher than reality so the ls function is used again
           LowUse = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           PercHomes = Homes/sum(EW2$Homes),
           Population = sum(Pop, na.rm= T),
           Poperc = Population/sum(EW2$Pop))

@@

z <-ChelseaLONDATA %>% 
  filter(LAD11CD =="E09000020") %>% 
  bind_rows(WestminsterLONDATA) %>%
  MakeLeaflet()

BradfordDATA %>% filter(LAD11NM=="Bradford") %>%
  MakeLeaflet

@@

cor(unaffordExLon$LowUsePerc, unaffordExLon$ratio)
cor(unaffordExLon$LowUsePerc, unaffordExLon$MedianPrice)
cor(unaffordExLon$Yearly.income, unaffordExLon$MedianPrice)
cor(unafford$Yearly.income, unafford$MedianPrice, "complete.obs")

@@

#This is no Longer useful due to using the whole percentile range 
# test <- 2:50 %>% 
#   map_df(~{
#   decile <- unaffordExLon %>%
#     mutate(decilev = ntile(ratio, .x)) %>%
#     filter(decilev == 1 | decilev == .x) %>%
#     group_by(decilev) %>%
#     summarise(mean = mean(LowUsePerc)) %>%
#     mutate(group = .x) %>%
#     spread(key = decilev, value = mean) %>%
#     setNames(c("group", "LowMean", "HighMean"))
#   
# }) 
# 
# test %>%
#   gather(key = type, value = mean, -group)%>%  
#   ggplot(aes(x = type, y = mean )) + geom_boxplot()
# 
# 
# test %>%
#   gather(key = type, value = mean, -group)%>% 
#   ggplot(aes(x = group, y = mean, colour = type )) + geom_point()
# 
# 
# test2 <- test %>%
#   mutate(ratio = HighMean/LowMean) 
# test2 %>%
#   ggplot(aes(x = group, y = ratio,)) + geom_point()
# 
# cor(test2$ratio, test2$group)

decile <- bind_rows(mutate(unaffordExLon, type = "Excl London"), 
                    mutate(unafford, type = "Inc London"),
                    mutate(unaffordLon, type = "London")) %>%
    group_by(type) %>%
    mutate(decile = ntile(ratio, 50)) %>%
      group_by(decile, type) %>%
    summarise(mean = mean(LowUsePerc),
              median = median(LowUsePerc),
              counts = n()
              )

@@

decile %>% ggplot() + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(x= decile, y = median, colour = type))

@@

data_frame(Index = 1:100) %>%
  mutate(Primary = exp(-0.05*(Index))+0.05, 
         Auxilary = (exp(Index/100)-1),
    Total = Primary + Auxilary) %>%
  gather(key = "Type", value = "value", -Index) %>%
  ggplot(aes(x= Index, y = value, colour = Type )) +
  geom_point() +
  labs(title = "LUP percentage as a function of primary and Auxilary demand",
       x = "Demand",
       y = "LUP percentage") +
  theme(
  axis.text.x = element_blank(),
  axis.text.y = element_blank()
  )

@@

#Overall price data 
```{r}
#Other property is massively more valuable on average than the rest of the property types
#mean value is 10 Million as such it has to be excluded
prices %>% group_by(X5) %>% 
  mutate(X2 = as.numeric(X2)) %>%
  summarise(count = n(),
            Value = sum(X2, na.rm =T),
            mean = mean(X2, na.rm = T)) %>%
mutate(countperc = (count/sum(count)),
       ValuePerc = Value/sum(Value))

#Looking at A and B property we can see that B properties are more expensive than A type
prices %>% group_by(X15) %>% 
  mutate(X2 = as.numeric(X2)) %>%
  summarise(count = n(),
            Value = sum(X2, na.rm =T),
            mean = mean(X2, na.rm = T)) %>%
mutate(countperc = (count/sum(count)),
       ValuePerc = Value/sum(Value))

#Other only appears in the B type sales never in A type
prices %>% 
  mutate(X2 = as.numeric(X2)) %>%
    group_by(X15, X5) %>% 
  summarise(count = n(),
            Value = sum(X2, na.rm =T),
            mean = mean(X2, na.rm = T)) %>%
  ungroup %>%
mutate(countperc = (count/sum(count)),
       ValuePerc = Value/sum(Value))  
```

@@

@@

#Linear
set.seed(1983)
MultiCheck <- 1:21 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

@@

  model <- rpart(Reference~ Extent + price + VacantsPerc+ PercRural,data=as.data.frame(TestResample))

@@

confusionMatrix(MultiCheck$Outcome, ModelMe$Reference)

@@

#random forest appears better than multilinear but when checked on many resamples it is worse... how? To much noise?
EnglandComp <- LADDep %>% 
  select (LAD11CD, LAD11NM = Local.Authority.District.name..2013., Extent)%>% 
  left_join(., Vacants, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD" = "Admin_district_code")) %>%
  left_join( LadHomes, by = "LAD11CD") %>%
  left_join(Rural, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes)

>>>>

#number of LUPS and Total Homes
DataCover <- ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  filter(!is.na(LAD11NM)) %>%
  summarise(
           TotalLADs = length(ls(pattern = "DATA", envir = globalenv())), #bits of other LADS cause the number to be higher than reality so the ls function is used again
           PercLADs = length(ls(pattern = "DATA", envir = globalenv()))/(EW2$LAD11NM %>% unique %>% length()),
           LowUse = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           PercHomes = Homes/sum(EW2$Homes),
           Population = sum(Pop, na.rm= T),
           PercPop = Population/sum(EW2$Pop)) %>%
  mutate_if(.<1, funs(signif(.,3))) %>%
  mutate_if(.>1, as.integer) %>%
  mutate_all(as.character) %>% 
  gather

DataCover

xtable(DataCover, caption="Summary of collected data coverage",
       label = "tab:DataCover") %>% 
  print(., type="latex", file=file.path(TexTables,"DataCover.tex"))

@@

z <-ChelseaLONDATA %>% 
  mutate(LAD11CD = ifelse(LAD11CD  == "E09000005", "E05009388" ,LAD11CD)) %>% #kept adding in Barnet
  filter(LAD11NM =="Kensington and Chelsea") %>% 
  MakeLeaflet()

mapshot(z, file = file.path(Figures, "Chelsea.pdf"))

CumbriaPlot <- ls(pattern = "CUMBRIA") %>% 
  map_df(~get(.x)) %>%
   group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

z<- MakeLeaflet(CumbriaPlot)

mapshot(z, file = file.path(Figures, "Cumbria.pdf"))

z<- MakeLeaflet(CornwallDATA)
mapshot(z, file = file.path(Figures, "Cornwall.pdf"))

z<- MakeLeaflet(BarrowCUMBRIADATA)
mapshot(z, file = file.path(Figures, "Barrow.pdf"))

@@

cor(unaffordExLon$LowUsePerc, unaffordExLon$ratio)
cor(unafford$Yearly.income, unafford$ratio, "complete.obs")

cor(unaffordExLon$LowUsePerc, unaffordExLon$MedianPrice)
cor(unaffordExLon$Yearly.income, unaffordExLon$MedianPrice)
cor(unafford$Yearly.income, unafford$MeanPrice, "complete.obs")

@@

decile <- bind_rows(mutate(unaffordExLon, type = "Excluding London"), 
                    mutate(unafford, type = "Including London"),
                    mutate(unaffordLon, type = "Only London")) %>%
    group_by(type) %>%
    mutate(decile = ntile(ratio, 50)) %>%
      group_by(decile, type) %>%
    summarise(mean = mean(LowUsePerc),
              median = median(LowUsePerc),
              counts = n()
              )

@@

decile %>% ggplot(aes(x= decile, y = median)) + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(colour = type))  +
  labs(x = "ith 2 percentile group", y = "median Percent Low Use") + 
  theme(legend.position= "none") + 
  geom_smooth(method="loess",se=FALSE, colour = "black")
SaveFig("LowUsePercVSratio.pdf")

unafford %>%
  ggplot(aes(x= ratio, y = MeanPrice)) + geom_point()

@@

data_frame(Index = 1:100) %>%
  mutate(Primary = exp(-0.05*(Index))+0.05, 
         Auxilary = (exp(Index/100)-1),
    Total = Primary + Auxilary) %>%
  gather(key = "Type", value = "value", -Index) %>%
  ggplot(aes(x= Index, y = value, colour = Type )) +
  geom_point() +
  labs(title = "LUP percentage as a function of primary and Auxilary demand",
       x = "Demand",
       y = "LUP percentage") +
  theme(
  axis.text.x = element_blank(),
  axis.text.y = element_blank()
  )
SaveFig("TheoreticalDemand.pdf")

@@

@@

#99% of the LADs are significantly different from 0 at the 95% level
sum(Combine1ExO$Ttest.p.value>0.975 |Combine1ExO$Ttest.p.value<0.025)/nrow(Combine1ExO)

PlotClassDiff(BootStrapRESExO$ChelseaLON, "Kensington and Chelsea")
SaveFig("ClassdiffChelsea.pdf")

PlotClassDiff(BootStrapRESExO$Cornwall, "Cornwall")
SaveFig("ClassdiffCornwall.pdf")

PlotClassDiff(BootStrapRESExO$BarrowCUMBRIA, "Barrow")
SaveFig("ClassdiffBarrow.pdf")

test <- BootStrapRESExO %>% 
  bind_rows %>%
  group_by(class, ID) %>%
  summarise_all(sum) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
        mutate(class = fct_relevel(class,c("Lower", "Mid", "Upper", "Prime", "Super")) )

test2 <- test %>% group_by(class) %>%
  summarise_all(mean)

PlotClassDiff(test)
SaveFig("ClassdiffAllData.pdf")

test %>% 
  mutate(RatioExvsAct = LowUsePrice/HomesPrice) %>%
   mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
     ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + 
     geom_boxplot() + 
     labs(title = "Observed within class difference in Price from expected for LUPs", 
          y = "% difference from expected")
SaveFig("PricediffAllData.pdf")

@@

#Linear
set.seed(1983)
MultiCheckL <- 1:21 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

@@

@@

confusionMatrix(MultiCheck$Outcome, ModelMe$Reference)
confusionMatrix(MultiCheckL$Outcome, ModelMe$Reference)

@@

#random forest appears better than multilinear but when checked on many resamples it is worse... how? To much noise?
EnglandComp <- LADDep %>% 
  select (LAD11CD, LAD11NM = Local.Authority.District.name..2013., Extent)%>% 
  left_join(., Vacants, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD" = "Admin_district_code")) %>%
  left_join( LadHomes, by = "LAD11CD") %>%
  #left_join(Rural, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes)
